---
title: "T-Test Problem"
author: "Jacob Welsh"
date: "27 February, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_0$ : no difference in average years of education between those who voted and those who did not vote  

$H_A$ : there is a difference in average years of education between those who voted and those who did not vote 

## Graphical Summary  

```{r}
plot(EDUC~VOTE12,data=Ourdata)
```

It appears that the average number of years is different. No group is 5 years, Yes group is about 8 or 9.  


## Numerical Summary  

```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```



## Inferential Test  

```{r}
t.test(EDUC~VOTE12,data=Ourdata)
```

## Conclusion

P-value from the t-test is 0.005, this is less than 0.05, so we reject the null hypothesis and conclude we have evidence that there is a differnce between the average years of education for those who voted in 2012 and those who did not vote in 2012.